---
title: "Caluculate MOCCS2score in R
author: "Ryosuke Matsuzawa"
output: BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{moccsR}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---


# Introduction


MOCCS2 is a method for detecting transcription factor recognition
sequences ([Yoshitane et al., 2019](https://doi.org/10.1038/s42003-019-0522-3))
and it was implemented in Perl
([Ozaki et al., 2016](https://doi.org/10.1016/j.compbiolchem.2016.01.014);
https://github.com/yuifu/moccs). This package allows MOCCS2 to be run in R.

# Installation and loading

You can install moccsR package with this command:

```{r eval = FALSE}
remotes::install_github("https://github.com/bioinfo-tsukuba/moccsR.git")
```

You can load moccsR package with this command:
```{r setup, message = FALSE}
library(moccsR)
```

# Data preparation

You can use ChIP-seq data as fasta file.
moccsR package has test data and You can obtain its
path with this command:
```{r}
fastaPath <- system.file("count.fasta", package = "moccsR")
```

# Caluculate MOCCS2score

You can calculate MOCCS2score with this command:
```{r}
calcMOCCS2score(fastaPath, k = 6, ignoreLowerCase = TRUE)
```

The parameter `fastaPath` represents the path to fasta file you want to run
with. `k` is length of mer (if you want to caluculate MOCCS2score of 6-mer, set
`k` to 6).
If parameter `ignoreLowerCase` is TRUE (default), moccsR ignores
lower-case characters in fasta file. This behavior assumes that repeat sequences
are represented in lower case in fasta files. You can include lower-case
characters setting `ignoreLowerCase` to `FALSE`.

# SessionInfo
```{r}
sessionInfo()
```